---
title: "fiddler_baby_crabbies_sizes"
author: "kelly"
format: html
editor: visual
execute: 
  warning: false
  message: false
---

```{r}
library(lterdatasampler)
library(tidyverse)
library(kableExtra)
```

-   In the Quarto doc, create an exploratory (unfinalized) plot of fiddler crab carapace widths observed at the different latitudes

```{r}
ggplot(data = pie_crab, aes(x = latitude, y = size)) +
        geom_point()+
 labs(caption = "this is my caption :)")
```

-   **Finalize the figure**. Add a figure caption using `#| fig-cap: "this is my caption"` in the code chunk where the graph is created. Update code chunk options (hint: `execute:` in YAML) so that only your finalized graph and figure caption show up in your knitted report (i.e., no code should show up)

-   To your document, add an unfinalized summary table containing the mean, standard deviation, and sample size of fiddler crab carapace widths by site (tip: use `round(mean(), 2)` to round a value to 2 decimal places)

```{r}
pie_crab %>%
 group_by(site) %>%
 summarize(mean_width = round(mean(size, na.rm=TRUE),2),
           sd_width = round(sd(size, na.rm = TRUE),2)) |> 
 kable(col.names = c("the place where the crab is...", "the mean of the width...", "the standard deviation of that thing dude..."))
 

```
